### 2020-03-23 paper/spores.tex
Changes to plain article format

\documentclass[conference]{IEEEtran}
%\documentclass[draftcls]{IEEEtran}
\pagestyle{plain}
\usepackage{import}
\usepackage{capt-of}
\usepackage[noend]{algpseudocode}
\usepackage{pifont}
\errorcontextlines\maxdimen

% begin vertical rule patch for algorithmicx (http://tex.stackexchange.com/questions/144840/vertical-loop-block-lines-in-algorithmicx-with-noend-option)
\makeatletter
% start with some helper code
% This is the vertical rule that is inserted
    \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\hspace*{.5em}\thealgruleextra\vrule height \thealgruleheight depth \thealgruledepth}}%
% its height and depth need to be adjustable
\newcommand*{\thealgruleextra}{}
\newcommand*{\thealgruleheight}{.75\baselineskip}
\newcommand*{\thealgruledepth}{.25\baselineskip}

\newcount\ALG@printindent@tempcnta
\def\ALG@printindent{%
    \ifnum \theALG@nested>0% is there anything to print
        \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
            % do nothing
        \else
            \unskip
            \addvspace{-1pt}% FUDGE to make the rules line up
            % draw a rule for each indent level
            \ALG@printindent@tempcnta=1
            \loop
                \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
                \advance \ALG@printindent@tempcnta 1
            \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
            \repeat
        \fi
    \fi
    }%
\usepackage{etoolbox}
% the following line injects our new indent handling code in place of the default spacing
\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
\makeatother

% the required height and depth are set by measuring the content to be shown
% this means that the content is processed twice
\newbox\statebox
\newcommand{\myState}[1]{%
    \setbox\statebox=\vbox{#1}%
    \edef\thealgruleheight{\dimexpr \the\ht\statebox+1pt\relax}%
    \edef\thealgruledepth{\dimexpr \the\dp\statebox+1pt\relax}%
    \ifdim\thealgruleheight<.75\baselineskip
        \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
    \fi
    \ifdim\thealgruledepth<.25\baselineskip
        \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
    \fi
    %\showboxdepth=100
    %\showboxbreadth=100
    %\showbox\statebox
    \State #1%
    %\State \usebox\statebox
    %\State \unvbox\statebox
    %reset in case the next command is not wrapped in \myState
    \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
    \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
}
% end vertical rule patch for algorithmicx

\input{preamble.tex}

\begin{document}
\input{contents.tex}
\end{document}

>>>>

\documentclass{article}
\input{preamble.tex}
\usepackage{authblk}

\begin{document}
\title{%
  \acs*{SPORES}: \acl*{SPORES}%
  %\name: Stateless Predictive Onion Routing for E-Squads%
  %% From the IEEE template
  % \thanks{Identify applicable funding agency here. If none, delete this.}
  % \thanks{%
  %   Daniel Bosk and Sonja Buchegger were funded by
  %   the Swedish Foundation for Strategic Research grant SSF FFL09-0086.
  %   Research done while Daniel Bosk visited the WIDE team at INRIA/IRISA Rennes, 
  %   France.
  % }
}

\author[1]{Daniel Bosk\thanks{%
  Research done while the author visited the WIDE team at INRIA/IRISA Rennes, 
  France.
}}
\affil[1]{KTH Royal Institute of Technology\\\email{daniel@bosk.se}}
\author[1]{Sonja Buchegger}
\author[2]{Adrien Luxey}
\affil[2]{Univ.\ de Rennes, INRIA, CNRS, IRISA\\\email{Adrien.Luxey@irisa.fr}}
\author[2]{Yérom-David Bromberg}
\author[2]{François Taïani}

\mode<article>{\maketitle}
\mode<presentation>{%
  \begin{frame}
    \maketitle
  \end{frame}
}

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\input{contents.tex}
\end{document}
